The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-07 SC-challenge.tex
Some edits on the related work

\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}

\katznote{Some ideas: \\
\url{https://softwaredatacitation.org/} \\
\url{http://www.software.ac.uk/software-credit}  \\
\url{http://astronomy-software-index.github.io/2015-workshop/} \\
\url{https://geodynamics.org/cig/projects/saga/} \\
maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group~\cite{Allen:2015ub}

\katznote{Arfon, are there more that showed up in related work in the software citation activity?}

@@

>>>>

While not a strictly machine-readable solution, Wilson in a blog post on the Software Sustainability Institute (SSI) website suggests that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.

Perhaps in recognition of the general desire to improve rates software citation, a number of workshops specifically aimed at addressing issues around software citation have been hosted (and sponsored) by funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) (~\cite{swdatacite}, ~\cite{ssisoftwarecredit}, ~\cite{aas-software-index}, ~\cite{saga}, ).

\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group~\cite{Allen:2015ub}

@@

\asnote{For key challenge `Determine standard practices for peer review of software':  we could cite the rOpenSci review process here: http://ropensci.org/blog/2016/03/28/software-review?}
